CKY Parsing With Independence Constraints

### 2015-05-16 paper.tex
Fix spelling mistakes

\begin{abstract}
The CKY algorithm is an important component in many natural language
parsers. We propose a novel type of constraint for context-free
parsing called independence constraints. Based on the concept
of independence between words, we show how these constraints can be
used to reduce the work done in the CKY algorithm. We demonstrate a
classifier which can be used to identify boundaries between
independent words in a sentence using only surface features, and show
that it can be used to speed up a CKY parser. We investigate the
tradeoff between speed and accuracy, and indicate directions for
improvement.
\end{abstract}

@@

The efficiency of the classifier is as important as the accuracy---it doesn't
matter how much time is saved during parsing if it takes even longer to run the
classifier. \texttt{opal} takes less than half a second to run on the instances from
section 22; however, the instances are created by a Python script, which is not
very optimized. This script takes about 100 seconds to run on the machine
described in Section \ref{sec:setup}. While this time is already less than the
time saved in the parser (see Section \ref{sec:parse-results}), it could be
significantly reduced by reimplementing in Java or even C++. Thus the potential
gains offered by this approach are not just theoretical.

@@

We used the modified Stanford Parser described above, with an unlexicalized
grammar\footnote{The grammar was extracted using the Stanford Parser with command-line options \texttt{-acl03pcfg -noRebinarization -compactGrammar 1}} extracted from the WSJ sections 02-21, and evaluated its performance
on section 22 using output from the clasifier as constraints. For the baseline,
the parser was given null constraints.

@@

A difference of 2 F$_{\text{1}}$ score is not small, but on the other hand it is
about by how much the unlexicalized Stanford Parser trails the Collins
parser, for example. However, as shown above in Section
\ref{sec:poly-classifier}, there is room to improve the linear
classifier through conjunctive features. As an indication of an upper
bound of the acheivable performance, we tried using the output of the
kernel classifier in the parser as above, while acknowledging that at
present the time needed to produce the classifier output dwarfs the
time needed to actually parse the test data.

@@

As a point of comparison, Roark et al. (2012) reported speedups of 1.6-2x with
no loss of accuracy. These results are not directly comparable due to
differences in parser (their parsers use beam search variants of CYK and
coarse-to-fine pruning) and grammar (they used the Berkeley latent variable
grammar and a lexicalized grammar).

@@

%}
\caption{Results from parsing section 22 using constraints from both linear and
polynomial classifiers, varying minimum sentence length and classifier
probability threshhold. }
\label{tbl:parse-results-full}
\end{table*}

>>>>

\begin{abstract}
The CKY algorithm is an important component in many natural language
parsers. We propose a novel type of constraint for context-free
parsing called independence constraints. Based on the concept
of independence between words, we show how these constraints can be
used to reduce the work done in the CKY algorithm. We demonstrate a
classifier which can be used to identify boundaries between
independent words in a sentence using only surface features, and show
that it can be used to speed up a CKY parser. We investigate the
trade-off between speed and accuracy, and indicate directions for
improvement.
\end{abstract}

@@

The efficiency of the classifier is as important as the accuracy---it doesn't
matter how much time is saved during parsing if it takes even longer to run the
classifier. \texttt{opal} takes less than half a second to run on the instances from
section 22; however, the instances are created by a Python script, which is not
very optimized. This script takes about 100 seconds to run on the machine
described in Section \ref{sec:setup}. While this time is already less than the
time saved in the parser (see Section \ref{sec:parse-results}), it could be
significantly reduced by re-implementing in Java or even C++. Thus the potential
gains offered by this approach are not just theoretical.

@@

We used the modified Stanford Parser described above, with an unlexicalized
grammar\footnote{The grammar was extracted using the Stanford Parser with command-line options \texttt{-acl03pcfg -noRebinarization -compactGrammar 1}} extracted from the WSJ sections 02-21, and evaluated its performance
on section 22 using output from the classifier as constraints. For the baseline,
the parser was given null constraints.

@@

A difference of 2 F$_{\text{1}}$ score is not small, but on the other hand it is
about by how much the unlexicalized Stanford Parser trails the Collins
parser, for example. However, as shown above in Section
\ref{sec:poly-classifier}, there is room to improve the linear
classifier through conjunctive features. As an indication of an upper
bound of the achievable performance, we tried using the output of the
kernel classifier in the parser as above, while acknowledging that at
present the time needed to produce the classifier output dwarfs the
time needed to actually parse the test data.

@@

As a point of comparison, Roark et al. (2012) reported speedups of 1.6-2x with
no loss of accuracy. These results are not directly comparable due to
differences in parser (their parsers use beam search variants of CKY and
coarse-to-fine pruning) and grammar (they used the Berkeley latent variable
grammar and a lexicalized grammar).

@@

%}
\caption{Results from parsing section 22 using constraints from both linear and
polynomial classifiers, varying minimum sentence length and classifier
probability threshold. }
\label{tbl:parse-results-full}
\end{table*}
